---
output: github_document
---

# FinalProjectG4
[Package Repository:FinalProjectG4] (https://github.com/AU-R-Programming/FinalProjectG4)

The package can be downloaded by using the `devtools::install_github` function. After downloading the package, we need to call the function called `g4lmfunc`. After activating the function it is ready to use. We will apply our function to the `crop.data.csv` dataset as an example. 

```{r echo=FALSE, message=FALSE, warning=FALSE}
library(g4lmfunc)
cropdata = read.csv("C:/Users/yagmu/Desktop/Auburn/Courses/Fall21/Stat6210/Github/FinalProjectG4/crop.data.csv")
```

Then we apply the `lm` function which is already available in `R`. We take the yield as response and density, block, fertilizer as predictors. 

```{r echo=FALSE, message=FALSE, warning=FALSE}
fitlm = lm(yield~density+block+fertilizer, data = cropdata)
summary(fitlm)
confint(fitlm)
par(mfrow = c(2,2))
plot(fitted(fitlm),residuals(fitlm))
abline(h=0, col = "pink")
```

Now, we apply our function `our_lm` to the same data.

